A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-03-03 analysis/paper/paper.Rmd
submit to JAS

We would like to thank the Yilan County Cultural Affairs Bureau in Taiwan for permitting access to the data used in this paper. We thank the excavation team of Kiwulan led by Yu-pei Chen for their post-excavation analysis and detailed documentation about burials that enable this study. We also thank Alberto Caimo and Steven M. Goodreau for the discussion regarding the methods at the earliest stage of analysis. This work was supported in part by the travel grant from the Department of Anthropology at the University of Washington and the Doctoral Dissertation Fellowship from the Chiang Ching-kuo Foundation for International Scholarly Exchange (Project #DF009-A-18). We thank Ben Fitzhugh and Peter Lape for their insightful comments on an early draft. We also acknowledge comments from anonymous reviewers that have greatly improved this manuscript.

>>>>

We would like to thank the Yilan County Cultural Affairs Bureau in Taiwan for permitting access to the data used in this paper. We thank the excavation team of Kiwulan led by Yu-pei Chen for their post-excavation analysis and detailed documentation about burials that enable this study. We also thank Alberto Caimo and Steven M. Goodreau for the discussion regarding the methods at the earliest stage of analysis. This work was supported in part by the travel grant from the Department of Anthropology at the University of Washington, the predissertation summer travel grant from the Henry Luce Foundation/ACLS Program in China Studies, and the Doctoral Dissertation Fellowship from the Chiang Ching-kuo Foundation for International Scholarly Exchange (Project #DF009-A-18). We thank Ben Fitzhugh and Peter Lape for their insightful comments on an early draft. We also acknowledge comments from anonymous reviewers that have greatly improved this manuscript.
